---
title: "IMDB_dataset"
author: "Z.CAI"
date: "2021年11月24日"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Classifiying Movie Reviews: A Binary Classification Example - the IMDB dataset 

loading the IMDB dataset
```{r}
library(keras)

imdb <- dataset_imdb(num_words = 10000)
c(c(train_data, train_labels), c(test_data, test_labels)) %<-% imdb
```
the multi_assignment (%<-%) operator equally: 

```{r}
imdb <- dataset_imdb(num_words = 10000)

train_data <- imdb$train$x 
train_labels <- imdb$train$y 
test_data <- imdb$test$x 
test_labels <- imdb$test$y

```


```{r}
str(train_data[[1]])

train_labels[[1]]
```

```{r}
max(sapply(train_data, max))
```

decodes into English words

```{r}
word_index <- dataset_imdb_word_index()
reverse_word_index <- names(word_index)
names(reverse_word_index) <- word_index

decoded_review <- sapply(train_data[[1]], function(index) {
  word <- if (index >= 3) reverse_word_index[[as.character(index - 3)]]
  if (!is.null(word)) word else "?" 
})
   
decoded_review
```


encoding the integer sequenes into a binary matrix 

```{r}
vectorise_sequences <- function(sequences, dimension = 10000) {
  results <- matrix(0, nrow = length(sequences), ncol = dimension) 
  for (i in 1:length(sequences))
    results[i, sequences[[i]]] <- 1 
  results
}

x_train <- vectorise_sequences(train_data) 
x_test <- vectorise_sequences(test_data)
```

```{r}
str(x_train[1,])
```

```{r}
y_train <- as.numeric(train_labels)
y_test <- as.numeric(test_labels)
```

the model definition 

```{r}
library(keras)

model <- keras_model_sequential() %>%
  layer_dense(units = 16, activation = "relu", input_shape = c(10000)) %>%
  layer_dense(units = 16, activation = "relu") %>%
  layer_dense(units = 1, activation = "sigmoid")
```
compiling the model 
```{r}
model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)
```

alternatively: configure the optimizer
```{r}
model %>% compile(
  optimizer = optimizer_rmsprop(lr=0.001),
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)
```

alternatively: using custom losses and metrics

```{r}
model %>% compile(
  optimizer = optimizer_rmsprop(lr=0.001),
  loss = "loss_binary_crossentropy",
  metrics = metric_binary_accuracy
)
```

setting aside a validation set

```{r}
val_indices <- 1:10000

x_val <- x_train[val_indices,]
partial_x_train <- x_train[-val_indices,]
y_val <- y_train[val_indices] 
partial_y_train <- y_train[-val_indices]
```

training the model

```{r}
model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)

history <- model %>% fit(
  partial_x_train,
  partial_y_train,
  epochs = 20,
  batch_size = 512,
  validation_data = list(x_val, y_val)
)
```
```{r}
str(history)
plot(history)

history_df <- as.data.frame(history)
str(history_df)
```
retraining a model from scratch

```{r}
model <- keras_model_sequential() %>%
  layer_dense(units = 16, activation = "relu", input_shape = c(10000)) %>%
  layer_dense(units = 16, activation = "relu") %>%
  layer_dense(units = 1, activation = "sigmoid")

model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy")
)

model %>% fit(x_train, y_train, epochs = 4, batch_size = 512)
results <- model %>% evaluate(x_test, y_test)

results
```
generate predictions on new data

```{r}
model %>% predict(x_test[1:10,])
```
