---
title: "Advanced_RNN_A_Temperature_Forecasting_Problem"
author: "Z.CAI"
date: "2022年1月12日"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
dir.create("C:/Users/CAI/Desktop/Deep_Learning_with_R/Advanced_RNN_A_Temperature_Forecasting_Problem/jena_climate", recursive = TRUE)

download.file(
"https://s3.amazonaws.com/keras-datasets/jena_climate_2009_2016.csv.zip",
"C:/Users/CAI/Desktop/Deep_Learning_with_R/Advanced_RNN_A_Temperature_Forecasting_Problem/jena_climate/jena_climate_2009_2016.csv.zip"
)

unzip("C:/Users/CAI/Desktop/Deep_Learning_with_R/Advanced_RNN_A_Temperature_Forecasting_Problem/jena_climate/jena_climate_2009_2016.csv.zip",
      exdir = "C:/Users/CAI/Desktop/Deep_Learning_with_R/Advanced_RNN_A_Temperature_Forecasting_Problem/jena_climate"
)
```

inspecting the data of the Jena weather dataset
```{r}
library(tibble)
library(readr)

data_dir <- "C:/Users/CAI/Desktop/Deep_Learning_with_R/Advanced_RNN_A_Temperature_Forecasting_Problem/jena_climate"
fname <- file.path(data_dir, "jena_climate_2009_2016.csv")
data <- read_csv(fname)

glimpse(data)
```

plotting the temperature timeseries
```{r}
library(ggplot2)
ggplot(data, aes(x = 1:nrow(data), y = `T (degC)`)) + geom_line()
```

plotting the first 10 days of the temperature timeseries
```{r}
ggplot(data[1:1440, ], aes(x = 1:1440, y = `T (degC)`)) + geom_line()
```

## Preparing the data

understanding generator functions(example)

```{r}
sequence_generator <- function(start) {
  value <- start - 1
  function() {
    value <<- value + 1
    value
  }
}

gen <- sequence_generator(10)
gen()
gen()
```

converting the data into a floating-point matrix
```{r}
data <- data.matrix(data[, -1])
str(data)
```

Normalising the data
```{r}
train_data <- data[1:200000, ]
mean <- apply(train_data, 2, mean)
std <- apply(train_data, 2, sd)
data <- scale(data, center = mean, scale = std)

str(data)
```

generator yielding timeseries samples and their targets
```{r}
generator <- function(data, lookback, delay,
                      min_index, max_index, 
                      shuffle = FALSE,
                      batch_size = 128,
                      step = 6) {
  if (is.null(max_index)) max_index <- nrow(data) - delay - 1
  i <- min_index + lookback
  function() {
    if (shuffle) {
      rows <- sample(c((min_index + lookback): max_index), size = batch_size)
    } else {
      if (i + batch_size >= max_index)
        i <<- min_index + lookback
      rows <- c(i:min(i + batch_size, max_index))
      i <<- i + length(rows)
    }
    
    samples <- array(0, dim = c(length(rows),
                                lookback / step,
                                dim(data)[[-1]]))
    targets <- array(0, dim = c(length(rows)))
    
    for (j in 1:length(rows)) {
      indices <- seq(rows[[j]] - lookback, rows[[j]] - 1, 
                     length.out = dim(samples)[[2]])
      samples[j,,] <- data[indices,]
      targets[[j]] <- data[rows[[j]] + delay, 2]
    }
    
    list(samples, targets)
  }
}

```

preparing the training, validation, and test generators
```{r}
library(keras)

lookback <- 1440
step <- 6
delay <- 144
batch_size <- 128

train_gen <- generator(
  data, 
  lookback = lookback,
  delay = delay,
  min_index = 1,
  max_index = 200000,
  shuffle = TRUE,
  step = step,
  batch_size = batch_size
)

val_gen = generator(
  data,
  lookback = lookback,
  delay = delay,
  min_index = 200001,
  max_index = 300000,
  step = step,
  batch_size = batch_size
)

test_gen <- generator(
  data,
  lookback = lookback,
  delay = delay,
  min_index = 300001,
  max_index = NULL,
  step = step,
  batch_size = batch_size
)

val_steps <- (300000 - 200000 - lookback) / batch_size

test_steps <- (nrow(data) - 300001 - lookback) / batch_size
```

## A common-sense, non-machine-learning baseline

mean(abs(preds - targets))

computing the common-sense baseline MAE
```{r}
evaluate_naive_method <- function() {
  batch_maes <- c()
  for (step in 1:val_steps) {
    c(samples, targets) %<-% val_gen()
    preds <- samples[, dim(samples)[[2]], 2]
    mae <- mean(abs(preds - targets))
    batch_maes <- c(batch_maes, mae)
  }
  print(mean(batch_maes))
}

evaluate_naive_method()
```

converting the MAE back to a Celsius error 
```{r}
celsius_mae <- 0.2783268 * std[[2]]
celsius_mae
```

## A basic machine-learning approach

training and evaluating a densely connected model 
```{r}
library(keras)

model <- keras_model_sequential() %>% 
  layer_flatten(input_shape = c(lookback / step, dim(data)[-1])) %>% 
  layer_dense(units = 32, activation = "relu") %>% 
  layer_dense(units = 1)

model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit_generator(
  train_gen,
  steps_per_epoch = 500,
  epochs = 20,
  validation_data = val_gen,
  validation_steps = val_steps
)
```

plotting results
```{r}
plot(history)
```


## A first recurrent baseline

training and evaluating a model with layer_GRU
```{r}
model <- keras_model_sequential() %>% 
  layer_gru(units = 32, input_shape = list(NULL, dim(data)[[-1]])) %>% 
  layer_dense(units = 1)

model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit_generator(
  train_gen,
  steps_per_epoch = 500,
  epochs = 20,
  validation_data = val_gen,
  validation_steps = val_steps
)
```

plotting result
```{r}
plot(history)
```


## Using recurrent dropout to fight overfitting

training and evaluating a dropout-regularised GRU-based model
```{r}
model <- keras_model_sequential() %>% 
  layer_gru(units = 32, dropout = 0.2, recurrent_dropout = 0.2,
            input_shape = list(NULL, dim(data)[[-1]])) %>% 
  layer_dense(units = 1)

model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit(
  train_gen,
  steps_per_epoch = 500,
  epochs = 40,
  validation_data = val_gen,
  validation_steps = val_steps
)
```

plotting result
```{r}
plot(history)
```

## Stacking recurrent layers

training and evaluating a dropout-regularised, stacked GRU model
```{r}
model <- keras_model_sequential() %>% 
  layer_gru(units = 32, 
            dropout = 0.1,
            recurrent_dropout = 0.5,
            return_sequences = TRUE,
            input_shape = list(NULL, dim(data)[[-1]])) %>% 
  layer_gru(units = 64, activation = "relu", 
            dropout = 0.1,
            recurrent_dropout = 0.5) %>% 
  layer_dense(units = 1)

model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit(
  train_gen,
  steps_per_epoch = 500,
  epochs = 40,
  validation_data = val_gen,
  validation_steps = val_steps
)
```

plotting result
```{r}
plot(history)
```

training a bidirectional GRU
```{r}
model <- keras_model_sequential() %>% 
  bidirectional(
    layer_gru(units = 32), input_shape = list(NULL, dim(data)[[-1]])
  ) %>% 
  layer_dense(units = 1)

model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit(
  train_gen,
  steps_per_epoch = 500,
  epochs = 40, 
  validation_data = val_gen,
  validation_steps = val_steps
)
```


## Combining CNNs and RNNs to process long sequences

training and evaluating a simple 1D convnet on the Jena data
```{r}
model <- keras_model_sequential() %>% 
  layer_conv_1d(filters = 32, kernel_size = 5, activation = "relu",
                input_shape = list(NULL, dim(data)[[-1]])) %>% 
  layer_max_pooling_1d(pool_size = 3) %>% 
  layer_conv_1d(filters = 32, kernel_size = 5, activation = "relu") %>% 
  layer_max_pooling_1d(pool_size = 3) %>% 
  layer_conv_1d(filters = 32, kernel_size = 5, activation = "relu") %>% 
  layer_global_max_pooling_1d() %>% 
  layer_dense(units = 1)

model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit(
  train_gen,
  steps_per_epoch = 500,
  epochs = 20,
  validation_data = val_gen,
  validation_steps = val_steps
)
```

```{r}
plot(history)
```

preparing higher-resolution data generators for the Jena dataset

```{r}
step <- 3
lookback <- 720
delay <- 144

train_gen <- generator(
  data,
  lookback = lookback,
  delay = delay,
  min_index = 1,
  max_index = 200000,
  shuffle = TRUE,
  step = step
)

val_gen <- generator(
  data,
  lookback = lookback,
  delay = delay,
  min_index = 200001,
  max_index = 300000,
  step = step
)

test_gen <- generator(
  data,
  lookback = lookback,
  delay = delay,
  min_index = 300001,
  max_index = NULL,
  step = step
)

val_steps <- (300000 - 200001 - lookback) / 128
test_steps <- (nrow(data) - 300001 - lookback) /128

```

model combining a 1D convolutional base and a GRU layer
```{r}
model <- keras_model_sequential() %>% 
  layer_conv_1d(filters = 32, kernel_size = 5, activation = "relu",
                input_shape = list(NULL, dim(data)[[-1]])) %>% 
  layer_max_pooling_1d(pool_size = 3) %>%
  layer_conv_1d(filters = 32, kernel_size = 5, activation = "relu") %>% 
  layer_gru(units = 32, dropout = 0.1, recurrent_dropout = 0.5) %>% 
  layer_dense(units = 1)

summary(model)
```

```{r}
model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit(
  train_gen,
  steps_per_epoch = 500,
  epochs = 20,
  validation_data = val_gen,
  validation_Steps = val_steps
)
```

```{r}
plot(history)
```























