---
title: "Generating_Images_with_Variational_Autoencoders"
author: "Z.CAI"
date: "2022年1月29日"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Variational autoencoders

c(z_mean, z_log_variance) %<% encoder(input_img)
z <- z_mean + exp(z_log_variance) * epsilon
reconstructed_img <- decoder(z)
model <- keras_model(input_img, reconstructed_img)

VAE encoder network
```{r}
library(keras)

img_shape <- c(28, 28, 1)
batch_size <- 16
latent_dim <- 2L 
input_img <- layer_input(shape = img_shape)

x <- input_img %>% 
  layer_conv_2d(filters = 32, kernel_size = 3, padding = "same",
                activation = "relu") %>% 
  layer_conv_2d(filters = 64, kernel_size = 3, padding = "same",
                activation = "relu", strides = c(2, 2)) %>% 
  layer_conv_2d(filters = 64, kernel_size = 3, padding = "same", 
                activation = "relu") %>% 
  layer_conv_2d(filters = 64, kernel_size = 3, padding = "same",
                activation = "relu")

shape_before_flattening <- k_int_shape(x)

x <- x %>% 
  layer_flatten() %>% 
  layer_dense(units = 32, activation = "relu")

z_mean <- x %>% 
  layer_dense(units = latent_dim)

z_log_var <- x %>% 
  layer_dense(units = latent_dim)
```

latent-space-sampling function
```{r}
sampling <- function(args) {
  c(z_mean, z_log_var) %<-% args
  epsilon <- k_random_normal(shape = list(k_shape(z_mean)[1], latent_dim),
                             mean = 0, stddev = 1)
  z_mean + k_exp(z_log_var) * epsilon
}

z <- list(z_mean, z_log_var) %>% 
  layer_lambda(sampling)
```

VAE decoder network, mapping latent space points to images
```{r}
decoder_input <- layer_input(k_int_shape(z)[-1])

x <- decoder_input %>% 
  layer_dense(units = prod(as.integer(shape_before_flattening[-1])),
              activation = "relu") %>% 
  layer_reshape(target_shape = shape_before_flattening[-1]) %>% 
  layer_conv_2d_transpose(filters = 32, kernel_size = 3, padding = "same",
                          activation = "sigmoid")
decoder <- keras_model(decoder_input, x)

z_decoded <- decoder(z)
```

custom layer used to compute the VAE loss
```{r}
library(R6)

CustomVariationalLayer <- R6Class("CustomVariationalLayer",
                                  
  inherit = KerasLayer,
                                  
  public = list(
                                  
    vae_loss = function(x, z_decoded) {
      x <- k_flatten(x)
      z_decoded <- k_flatten(z_decoded)
      xent_loss <- metric_binary_crossentropy(x, z_decoded)
                                      
      kl_loss <- -5e-4 * k_mean(
        1 + z_log_var - k_square(z_mean) - k_exp(z_log_var),
        axis = -1L
      )
      k_mean(xent_loss + kl_loss)
    },
    
    call = function(inputs, mask = NULL) {
      x <- inputs[[1]]
      z_decoded <- inputs[[2]]
      loss <- self$vae_loss(x, z_decoded)
      self$add_loss(loss, inputs = inputs)
      x
    }
  )
)

layer_variational <- function(object) {
  create_layer(CustomVariationalLayer, object, list())
}

y <- list(input_img, z_decoded) %>% 
  layer_variational()

```

training the VAE
```{r}
vae <- keras_model(input_img, y)

vae %>% compile(
  optimizer = "rmsprop",
  loss = NULL
)

mnist <- dataset_mnist()
c(c(x_train, y_train), c(x_test, y_test)) %<-% mnist

x_train <- x_train / 255
x_train <- array_reshape(x_train, dim = c(dim(x_train), 1))

x_test <- x_test / 255
x_test <- array_reshape(x_test, dim = c(dim(x_test), 1))

vae %>% fit(
  x = train, y = NULL,
  epochs = 10, 
  batch_size = batch_size,
  validation_data = list(x_test, NULL)
)
```

smapling a grid of points from the 2D latent space and decoding them to images
```{r}
n <- 15
digit_size <- 28

grid_x <- qnorm(seq(0.05, 0.95, length.out = n))
grid_y <- qnorm(seq(0.05, 0.95, length.out = n))

op <- par(mfrow = c(n, n), mar = c(0,0,0,0), bg = "black")
for (i in 1:length(grid_x)) {
  yi <- grid_x[[i]]
  for (j in 1:length(grid_y)) {
    xi <- grid_y[[j]]
    z_sample <- matrix(c(xi, yi), nrow = 1, ncol = 2)
    z_sample <- t(replicate(batch_size, z_sample, simplify = "matrix"))
    x_decoded <- decoder %>% predict(z_sample, batch_size = batch_size)
    digit <- array_reshape(x_decoded[1,,,], dim = c(digit_size, digit_size))
    plot(as.raster(digit))
  }
}

par(op)
```























