---
title: "Neural_Style_Transfer"
author: "Z.CAI"
date: "2022年1月28日"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

loss <- distance(style(reference_image) - style(generated_image)) + 
        distance(content(original_image) - content(generated_image))

## Neural style transer in keras

In strsplit(x, "\n") : input string 1 is invalid in this locale
```{r}
sessionInfo()

Sys.getlocale()

Sys.setlocale("LC_ALL", "English")
```

defining initial variables
```{r}
library(keras)

target_image_path <- "C:/Users/CAI/Desktop/Deep_Learning_with_R/Generative Deep Learning/Neural_Style_Transfer/img/portrait.png"

style_reference_image_path <- "C:/Users/CAI/Desktop/Deep_Learning_with_R/Generative Deep Learning/Neural_Style_Transfer/img/transfer_style_reference.png"

img <- image_load(target_image_path)
width <- img$size[[1]]
height <- img$size[[2]]
img_nrows <- 400
img_ncols <- as.integer(width * img_nrows / height)
```

auxiliary functions
```{r}
preprocess_image <- function(path) {
  img <- image_load(path, target_size = c(img_nrows, img_ncols)) %>% 
    image_to_array() %>% 
    array_reshape(c(1, dim(.)))
  imagenet_preprocess_input(img)
}

deprocess_image <- function(x) {
  x <- x[1,,,]
  x[,,1] <- x[,,1] + 103.939
  x[,,2] <- x[,,2] + 116.779
  x[,,3] <- x[,,3] + 123.68
  x <- x[,,c(3,2,1)]
  x[x > 255] <- 255
  x[x < 0] <- 0
  x[] <- as.integer(x) /255
  x
}

```

loading the pretrained VGG19 network and applying it to the three images
```{r}
target_image <- k_constant(preprocess_image(target_image_path))
style_reference_image <- k_constant(
  preprocess_image(style_reference_image_path)
)

combination_image <- k_placeholder(c(1, img_nrows, img_ncols, 3))

input_tensor <- k_concatenate(list(target_image, style_reference_image, 
                                   combination_image), axis = 1)

model <- application_vgg19(input_tensor = input_tensor,
                           weights = "imagenet",
                           include_top = FALSE)

cat("Model loaded\n")
```

content loss
```{r}
content_loss <- function(base, combination) {
  k_sum(k_square(combination - base))
}
```

style_loss 
```{r}
gram_matrix <- function(x) {
  features <- k_batch_flatten(k_permute_dimensions(x, c(3, 1, 2)))
  gram <- k_dot(features, k_transpose(features))
  gram
}

style_loss <- function(style, combination) {
  S <- gram_matrix(style)
  C <- gram_matrix(combination)
  channels <- 3
  size <- img_nrows * img_ncols
  k_sum(k_square(S - C)) / (4 * channels^2 * size^2)
}
```

total variation loss
```{r}
total_variation_loss <- function(x) {
  y_ij <- x[, 1:(img_nrows - 1L), 1:(img_ncols - 1L),]
  y_i1j <- x[, 2:(img_nrows), 1:(img_ncols - 1L),]
  y_ij1 <- x[, 1:(img_nrows - 1L), 2:(img_ncols),]
  a <- k_square(y_ij - y_i1j)
  b <- k_square(y_ij - y_ij1)
  k_sum(k_pow(a + b, 1.25))
}
```

defining the final loss that you will minimize
```{r}
outputs_dict <- lapply(model$layers, `[[`, "output")
names(outputs_dict) <- lapply(model$layers, `[[`, "name")

content_layer <- "block5_conv2"
style_layers <- c("block1_conv1", "block2_conv1", 
                 "block3_conv1", "block4_conv1", 
                 "block5_conv1")

total_variation_weight <- 1e-4
style_weight <- 1.0
content_weight <- 0.025

loss <- k_variable(0.0)
layer_features <- outputs_dict[[content_layer]]
target_image_features <- layer_features[1,,,]
combination_features <- layer_features[3,,,]
loss <- loss + content_weight * content_loss(target_image_features,
                                             combination_features)

for (layer_name in style_layers) {
  layer_features <- outputs_dict[[layer_name]]
  style_reference_features <- layer_features[2,,,]
  combination_features <- layer_features[3,,,]
  s1 <- style_loss(style_reference_features, combination_features)
  loss <- loss + ((style_weight / length(style_layers)) * s1)
}

loss <- loss + 
  (total_variation_weight * total_variation_loss(combination_image))
```

setting up the gradient-dscent process
```{r}
grads <- k_gradients(loss, combination_image) [[1]]

fetch_loss_and_grads <- k_function(list(combination_image), list(loss, grads))

eval_loss_and_grads <- function(image) {
  image <- array_reshape(image, c(1, img_nrows, img_ncols, 3))\
  outs <- fetch_loss_and_grads(list(image))
  list(
    loss_value = outs[[1]],
    grad_values = array_reshape(outs[[2]], dim = length(outs[[2]]))
  )
}

library(R6)

Evaluator <- R6Class("Evaluator",
                     public = list(
                       loss_value = NULL,
                       grad_values = NULL,
                       initialize = function() {
                         self$loss_value <- NULL
                         self$grad_values <- NULL
                       },
                       loss = function(x) {
                         loss_and_grad <- eval_loss_and_grads(x)
                         self$loss_value <- loss_and_grad$loss_value
                         self$grad_values <- loss_and_grad$grad_values
                         self$loss_value
                       },
                       grads = function(x) {
                         grad_values <- self$grad_values
                         self$loss_value <- NULL
                         self$grad_values <- NULL
                         grad_values
                       }
                      )
                    )

evaluator <- Evaluator$new()
```

style-transfer loop
```{r}
iterations <- 20

dms <- c(1, img_nrows, img_ncols， 3)

x <- preprocess_image(target_image_path)

x <- array_reshape(x, dim = length(x))

for (i in 1:iterations) {
  
  opt <- optim(
    array_reshape(x, dim = length(x)),
    fn = evaluator$loss,
    gr = evaluator$grads,
    method = "L-BFGS-B",
    control = list(maxit = 15)
  )
  
  cat("Loss:", opt$value, "\n")
  
  image <- x <- opt$par
  image <- array_reshape(image, dms)
  
  im <- deprocess_image(image)
  plot(as.raster(im))
}

```




















